Can we use masked priming in an online setting?

### 2021-04-27 Lab meeting presentation April 2021.Rmd
Start presentation

---
title: "Online masked priming"
subtitle: "Can we get the same quality data as in a laboratory study?"
author: "Bernhard Angele, Pablo Gomez, & Manuel Perea"
institute: "Bournemouth/Valencia/San Bernardino/The Internet"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(sp)
library(leaflet)
library(lmerTest)
library(tidyverse)
library(cowplot)
library(stargazer)
source("RainCloudPlots.R")
```

@@

# Our experiment

@@

Design

@@

Participants

```{r participant_map, echo = FALSE, message=FALSE}

participant_data <- read_csv("participant_data.csv")
coordinates(participant_data) <- c("Location Longitude","Location Latitude")
leaflet(participant_data) %>% addMarkers(label = .$`Confirm Prolific ID`) %>% addTiles()
```

# Results

```{r main_code, echo = FALSE, warning=FALSE, message = FALSE}

csv_data <- fs::dir_ls(path = "./data", glob = "*.csv") %>%
  map_dfr(read_csv, .id = "source", col_type = cols(
  .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer())) %>% 
  filter(!is.na(TrialID) & TrialID < 1000) %>%
  select(source, participant, date, OS, frameRate, rt, corr, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target)

# get participants with correct responses

accuracy_by_participant <- csv_data %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n())

participants_to_include <- accuracy_by_participant %>% filter(N == 480 & acc > .8)

participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")
paste0(participant_list_for_prolific, sep = "\n") %>% writeClipboard() # works on windows

# for now, we only have two participants with accuracy > .8 and a full data set

data_to_include <- csv_data %>% filter(source %in% participants_to_include$source) %>% mutate(StimulusType = StimulusType %>% factor, Condition = Condition %>% factor, PrimeDuration = PrimeDuration %>% factor, rt = rt * 1000)

write_csv(data_to_include, path = "current_data.csv")

data_summary_rt <- data_to_include %>% group_by(StimulusType, Condition, PrimeDuration) %>% summarise(M = mean(rt), SD = sd(rt), N = n())

# data above 1500 ms excluded

plot_raincloud(data_to_include %>% filter(corr == 1 & rt < 1500), x_column = "Condition", y_column = "rt", x_label = "Condition", y_label = "RT in ms (correct responses)", main_title = "RT by condition and word type") + 
  # put labels on the mean for easier comparison
  stat_summary(fun.data = function(x) {data.frame(label = format(mean(x), digits = 2), y = mean(x))}, 
                                      geom = "text",
                                      #width = 1,
                                      position = position_nudge(x = 0.5, y = 0),
                                      #size = 0.2,
                                      color = "black") +
  facet_grid(cols = vars(PrimeDuration), rows = vars(StimulusType), labeller = label_context)

```

---
# LMM for RT (words, correct responses)
```{r lmms}
lmm1 <- lmer(data = data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500), rt ~ Condition * PrimeDuration + (Condition+PrimeDuration|source) + (PrimeDuration|Target))

summary(lmm1)

```

---
# gLMM for accuracy (Words)
```{r logistic_lmm}
lmm_acc <- glmer(data = data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt < 1500), corr ~ Condition + PrimeDuration + (1|Target), family = binomial(link = "logit"))

summary(lmm_acc)

```

>>>>

---
title: "Can we use masked priming in an online setting?"

subtitle: "The effect of prime exposure duration in online masked priming lexical decision"
author: "Bernhard Angele, Ana Baciero, Pablo Gomez, & Manuel Perea"
institute: "Bournemouth University, Universidad Nebrija, DePaul University, California State University San Bernardino, Universitat de Valencia"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

# Our study

@@

# Design

## Experiment 1

@@

---
# Design

## Experiment 2

  - Like Experiment 1, but shorter prime duration condition (16 ms vs. 33 ms):
    - Targets: same 240 words and 240 nonwords
    - Conditions: 
      - prime duration (16 vs. 33 ms)
        - this corresponds to 1 vs. 2 refresh cycles at 60 Hz
      - prime condition: identical vs. unrelated
    - 60 word/nonword stimuli per group

---
# Results
